---
title: "TidyTemplate"
date: 2020-10-06
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}


tt <- tt_load("2020-10-06")



tt$tournament


```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt$tournament %>% View()

```

# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

tt$tournament %>% 
  group_by(year) %>% 
  summarize(reg=mean(reg_percent),
            games=mean(reg_w+reg_l)) %>% 
  ggplot() +
  geom_line(aes(x=year, y=games))
  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 




```{r}

#set fonts
textsize<-16
textfamily<-"Rockwell"

p3 <- tt$tournament %>%
  filter(tourney_finish!="OR") %>%
  mutate(champ=if_else(tourney_finish=="Champ", 1, 0)) %>% 
  group_by(school) %>% 
  mutate(c_total=round(sum(champ))) %>% 
  group_by(c_total) %>% 
  mutate(c_label=if_else(c_total>2, 
                         paste0("(",paste(unique(school),
                                              collapse=","),")"), 
                         paste0("(", n_distinct(school), " schools)")),
    championships = paste0(c_total, " ", c_label)) %>% 
  arrange(desc(championships)) %>% 
  mutate(championships=forcats::as_factor(championships)) %>% 
  ungroup() %>% 
  mutate(tourney_finish = recode_factor(tourney_finish,
                                "OR"="Opening round (1983 only)",
                                "1st"="First-round", 
                                "2nd"="Second-round",
                                "RSF"="Sweet 16",
                                "RF"="Elite Eight", 
                                "NSF"="Semifinals", 
                                "N2nd"="Runner-up", 
                                "Champ"="National Champions", 
                                .ordered=TRUE, .missing = "no data")) %>% 
  ggplot(aes(x=tourney_finish, y=reg_percent))+
  see::geom_violinhalf(position = position_nudge(x = .35, y = 0), fill="grey80", color="grey70")+
  geom_point(aes(color=championships),
             position = position_jitter(width = .25, height=0.18), size = 2, alpha=0.4) +
  scale_color_manual(values = c("slategray","#68B56A","#F8DE3E","#FF8200","blue"),
  guide=guide_legend(title="All-Time School Championships",
                     title.position = "top", title.hjust = 0.5, override.aes = list(size=4))) +
  labs(x="",
       y="Regular Season Win Percentage",
       caption="Excluding 1983 Opening Round. Source: FiveThirtyEight",
       title="  NCAA Women's Basketball Tournaments, 1982-2018",
       subtitle = str_wrap("    Team finish by all-time school championships and regular season win percentage",150)) + 
  scale_y_continuous(labels=scales::percent_format(scale = 1)) +
  expand_limits(y = 105) +
  coord_flip() +
  theme_minimal() +
  theme(legend.position="top",
        legend.justification='centre',
        legend.direction='horizontal',
     #   plot.title.position="plot",
        plot.title=element_text(hjust=0.5),
        plot.subtitle=element_text(hjust=0.5),
        plot.background = element_rect(fill="#FFF7F1"),
        text = element_text(family=textfamily, size = textsize)
        ) +
  annotate(
    geom = "curve", x = "Sweet 16", y = 46, xend = "First-round", yend = 43, 
    curvature = .5, arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(geom = "text", size= (textsize/4), family=textfamily,
           x = "Sweet 16", y = 47, label = str_wrap("No Team Under .550 Advanced To Second Round", 20), hjust = "left") +
  annotate(geom = "text", x= "National Champions", 
           size= (textsize/4), family=textfamily,
           y=60, label=str_wrap("'97 Tennessee Vols, lowest win % of any champion", 30)) +
    annotate(
    geom = "curve", x = "National Champions", y = 64, xend = "National Champions", yend = 69, 
    curvature = .3, arrow = arrow(length = unit(2, "mm"))
  ) +
    geom_rect(xmax = Inf,
              xmin = "Runner-up",
    ymin=101, ymax=106, color="grey20", fill="grey90",alpha=0.01) +
  annotate(geom="text", x= "National Champions",y=103.5, size= (textsize/4), family=textfamily,
           label=str_wrap("Of the 8 champions w/ perfect seasons, 6 were UConn", 10))
  

# textsize<-13
# textfamily<-"Rockwell"

library(ragg)

# colors()

tt$tournament %>% 
  filter(full_percent==100) %>% View()

library(systemfonts)
df<-system_fonts() 
df$family %>% unique() %>% sort()


font_info('Rockwell')

```


```{r}
#create layout

library(ragg)
library(patchwork)


# dev.set(dev.next())
# while (!is.null(dev.list()))  dev.off()


#Finish!
agg_png("p3.png", width = 1000, height = 800, units = 'px')
p3
dev.off()

```

