---
title: "TidyTemplate"
date: 2021-05-11
output: html_output
editor_options: 
  chunk_output_type: console
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
# install.packages("zipcodeR")
library(zipcodeR)
# devtools::install_github("laresbernardo/lares")

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-05-11")
tt$broadband %>% 
  head()
tt
```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

wifi<-tt$broadband %>% 
  janitor::clean_names() %>% 
  mutate("countycode"=as.double(county_id))

#from countyhealthrankings 
#https://www.countyhealthrankings.org/explore-health-rankings

url<-"https://www.countyhealthrankings.org/sites/default/files/media/document/analytic_data2021.csv"
lifeExp_names<-read_csv(url, n_max=1) 


lifeExp<-read_csv(url, skip = 2, 
                  col_names=colnames(lifeExp_names)) %>% 
        janitor::clean_names() %>% 
        filter(county_fips_code!="000") %>% 
        select(name,contains("state"),contains("fips"),contains("raw"))



lifeExp %>% head()

wifi
  
```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

wifi_life<-lifeExp %>% 
  # select(state, county, statecode, countycode, "life_exp_2019"=v147_rawvalue, "hs_2019"=v168_rawvalue) %>% 
  # mutate(statecounty=as.double(paste0(state_fips_code,county_fips_code))) %>% 
  mutate("countycode"=as.double(x5_digit_fips_code) ) %>% 
  left_join(wifi, by=c("countycode")) %>% 
  mutate(across(contains("broadband"), as.double))


wifi_life
  
wifi_life %>% 
  # mutate(life_exp_2019=round(life_exp_2019, 2)) %>% 
  # select(-contains("usage")) %>% 
  # drop_na() %>%
  ggplot(aes(y=flu_vaccinations_raw_value, x=broadband_usage)) +
  geom_jitter(alpha=0.3) +
  # ylim(0,0.004) +
  geom_smooth(method="loess") +
  theme_minimal()

  


```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

colnames(wifi_life)

wifi_life %>% 
  filter(flu_vaccinations_raw_value<0.4 & broadband_usage>0.73)

wifi_life %>% 
  slice_max(flu_vaccinations_raw_value, n=1)

```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
library(lares)

wifi_corrs<-wifi_life
  select(county_id, broadband_usage,median_household_income_raw_value,
         percent_rural_raw_value, insufficient_sleep_raw_value) 
  # select(county_id, broadband_usage, !contains("percent"))

corr_var(wifi_corrs, # name of dataset
  broadband_usage, # name of variable to focus on
  method="pearson"
  # top = 5,   # method = "pearson" # display top 5 correlations
) 

test<-wifi_life %>% select(broadband_usage, insufficient_sleep_raw_value) %>% drop_na()




```


```{r}

wifi_nest<-wifi_life %>% 
  select(state_abbreviation, county_name, county_id, broadband_usage, 
         premature_death_raw_value, where(is.numeric)) %>%
  mutate(county_id=as.character(county_id)) %>% 
  pivot_longer(cols=premature_death_raw_value:last_col(),
               names_to="ind",
               values_to="ind_value") %>% 
  mutate(ind=str_remove_all(ind, "_raw_value")) %>% 
  group_by(ind) %>% 
  nest()


corr_fun<-function(df) suppressMessages(cor.test(df$broadband_usage, df$ind_value, method = "spearman"))  %>% broom::tidy()

wifi_nest

wifi_nest <- mutate(wifi_nest, model = map(data, corr_fun))

wifi_results<-wifi_nest %>% 
  unnest(model)

wifi_results %>% 
  filter(p.value>0.01)


wifi_bars<-wifi_results %>% 
  ungroup() %>% 
  select(-data) %>% 
  # slice_max(abs(estimate), n = 30) %>%
  mutate(signif = case_when(p.value < 0.0001 ~ "***", 
                            p.value < 0.001 ~ "**",
                            p.value < 0.01 ~ "*",
                            TRUE ~ ""),
         direction=if_else(estimate>0, "pos","neg"),
         abs_corr=abs(estimate), 
         estimate=round(estimate, 3)) %>% 
    # arrange(estimate)
  select(ind, estimate, signif, direction, abs_corr) %>% 
  filter(str_detect(ind, "motor|rural|exercise|infant|median|flu|sleep|inact|reading")) %>% 
  mutate(ind=str_to_title(str_replace_all(ind, "_", " ")))
  



```



```{r}

library(ggtext)
font_add_google("Ubuntu","ubuntu")

basechart<-wifi_bars %>% 
    ggplot() +
      geom_col(aes(x=reorder(ind, abs_corr), y=abs_corr, fill=direction), width=0.9) + 
      geom_text(aes(x=reorder(ind, abs_corr), y=abs_corr-0.04, 
                    label=round(estimate, 3)), color="grey90") +
      scale_fill_discrete_diverging() +
      coord_flip(expand = FALSE)

basechart

basechart +
  theme_minimal() +
  theme(legend.position = "null",
       plot.title.position = "plot",
       plot.caption.position = "plot",
       text=element_text(family="ubuntu"),
        plot.background = element_rect(fill="ghostwhite",color=NA),
        legend.background = element_rect(fill="ghostwhite",color=NA),
        panel.background = element_rect(fill="ghostwhite", color=NA)) +
  labs(y="Estimated Correlation Coefficient (Absolute)",
       x="",
       title="Correlated Factors of Broadband Usage in US Counties (2019)",
       subtitle="Spearman Rank Correlation, Select Variables, p < 0.0001 ",
       caption="Data: Microsoft | countyhealthrankings.org")



```

```{r}

wifi_dots<-wifi_life %>% 
  select(name, state_abbreviation, "fluvax"=flu_vaccinations_raw_value ,broadband_usage) %>% 
  mutate(hlight=case_when(str_detect(name, "Travis") ~ "1",
                          fluvax==max(fluvax, na.rm=T) ~"1",
                          fluvax < 0.4 & broadband_usage>0.74 ~ "1",
                          TRUE ~ "0"))
wifi_dots %>% 
  ggplot(aes(y=fluvax, x=broadband_usage, color=hlight)) +
  geom_jitter(alpha=0.5) +
    geom_smooth(method="loess",color="orange", fill="yellow2") +
  scale_color_manual(values=c("grey50","blue")) +
  ggrepel::geom_text_repel(
    data = wifi_dots %>% filter(hlight=="1"),
    aes(label = paste0(name, ", ",state_abbreviation)),
    colour = "blue",
    family="ubuntu",
    min.segment.length = 0,
    segment.colour = "blue"
  ) +
  # ylim(0,0.004) +
  theme_minimal() +
    theme(legend.position = "null",
       plot.title.position = "plot",
       plot.caption.position = "plot",
       text=element_text(family="ubuntu"),
        plot.background = element_rect(fill="ghostwhite",color=NA),
        legend.background = element_rect(fill="ghostwhite",color=NA),
        panel.background = element_rect(fill="ghostwhite", color=NA)) +
  labs(y="Annual Flu Vaccinations, 2018 (%)",
       x="Broadband Usage, 2019 (%)",
       title="Is Broadband Usage Associated with Flu Vaccinations?",
       subtitle=str_wrap("The share of a US county's free-for-service Medicare enrollees who receive annual flu vaccines is correlated with it's broadband usage, although there are notable outliers",75),
       caption="Data: Microsoft | countyhealthrankings.org")



```


# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
