---
title: "TidyTemplate"
date: 2020-10-19
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

#install.packages("usmap")
# install.packages("tidygeocoder")

library(tidygeocoder)
library(tidyverse)
library(tidytuesdayR)
library(usmap)
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2020-10-20")
beer_awards <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-10-20/beer_awards.csv')

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

beer_awards %>% group_by(category, year) %>% count(sort=T) %>% filter(n<2)

beer_awards %>% 
  count(category, sort=T)
  
beer_awards %>% 
  filter(str_detect(city, "Louisville"))
```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

#separate pale ales and others


##create the data
data <- beer_awards %>% 
  mutate(IPA=if_else(str_detect(category, "Pale Ale|Blonde|Golden"), 
                     "All Pale Ales, Blondes, & IPAs", "Other Beers")) %>% 
  filter(!state %in% c("AK","HI")) %>% 
  mutate(city=str_replace(city, "\\((.*)\\)", "")) %>% #take out parentheses 
  mutate(city=str_replace(city, ".*/", "")) %>%  #slashes
  mutate(city=str_replace(city, "E2=80=8E", "")) 


# geocode the cities
lat_longs <- beer_awards %>%
  select(city, state) %>% 
  distinct() %>% #just get distinct cities to save geocoding API
  mutate(centroid=F) %>% 
  geocode(state=state, city=city, country="USA", 
          method = 'osm', lat = latitude , long = longitude) 

#filter out those that are missing and do centroid
lat_longs_missed<-lat_longs %>% 
  filter(is.na(latitude)) %>%
  select(-starts_with("l")) %>% 
  mutate(centroid=T) %>% 
  geocode(state=state, country="USA",
          method = 'osm', lat = latitude , long = longitude)

lat_longs<-lat_longs %>% 
  filter(!is.na(latitude)) %>% 
  bind_rows(lat_longs_missed)


#now merge back with data

map_data_raw <- data %>% 
  left_join(lat_longs, by=c("city","state")) %>% 
  filter(longitude< -50 & latitude<55)

map_data<- map_data_raw %>% 
  add_count(city, state, IPA) %>% #count by city state year
  ungroup() %>% 
  filter(centroid==F)

map_data

beer_awards %>% 
  filter(str_detect(category, "Golden")) %>% distinct(category) %>% print()
  
```



         
```{r calculate clusters}
# install.packages("dbscan")
library(dbscan)

EPS <- 1
clusters <- dbscan(select(map_data, latitude, longitude), minPts=5, eps = EPS)
map_data$cluster <- clusters$cluster

#groups vs noise
map_data<-map_data %>% 
  add_count(cluster, name="csize", sort = TRUE)
groups  <- map_data %>% filter(cluster != 0 & csize >= 10)
noise  <- map_data %>% filter(cluster == 0 | csize < 10)


top_cluster_cities<-map_data %>% 
  select(city, state, IPA, latitude, 
         longitude, year, n, cluster, csize) %>% 
  ungroup() %>% 
  group_by(cluster) %>% 
  mutate(max_n=max(n),
         max_city=if_else(n==max_n, str_c(city, ", ",state), "")) %>% 
  filter(max_city!="") %>% 
  ungroup() %>% 
  select(cluster, max_n, max_city) %>% distinct()
  

top_cluster_cities


top_cluster_IPA<-map_data %>% 
  ungroup() %>% 
  distinct(city, state, .keep_all=T) %>% #distinct cities
  group_by(cluster, IPA) %>%  #group by cluster and IPA level
  summarize(cluster_IPA_size=sum(n)) %>%  #total up all medals at cluster IPA
  select(cluster, IPA, cluster_IPA_size) %>% 
  ungroup() %>% 
  group_by(IPA) %>% 
  slice_max(order_by = cluster_IPA_size, n=5) %>% 
  left_join(top_cluster_cities, by="cluster")

top_cluster_IPA


```


```{r map clusters}
## Get colors for the map

library(randomcoloR)
# set.seed(127)
cols<-unique(groups$cluster)
colscale<-randomColor(count = length(cols), luminosity = c("bright"))

colscale <- setNames(colscale, cols)


library(ragg)
library(systemfonts)



mapfacet<-ggplot(map_data, aes(longitude, latitude)) + 
  borders("state", colour="grey60", fill="grey30") +
  geom_point(aes(fill = "black", size=n), shape=1, alpha=0.5, noise) +
  geom_point(aes(colour = as.factor(cluster), size=n), fill=NA, shape=1, groups) +
  # ggrepel::geom_label_repel(aes(label=city_total, colour=as.factor(cluster)),
  #            size=2, top_cities) +
  # geom_label(aes(label=city_total, colour=as.factor(cluster)),
  #            size=2, top_cities) +
  scale_size_continuous(range=c(1, 12)) +
  scale_color_manual(values=colscale) +
  facet_wrap(~IPA, ncol=1) +
  coord_map() +
  theme_void() +
  labs(title="Medals By Brewery Location and Beer Type, Colored by Cluster") +
  theme(legend.position = "none", 
          strip.text = element_text(color="white",  family="Candara", face="bold", size=14),
          plot.title=element_text(color="white", family="Candara", face="bold", hjust=0.5, size=14, margin=margin(0,5,0,0)),
          panel.border = element_blank(),
          plot.background = element_rect(color=NA, fill = "#3c3c3c"),
          panel.background = element_rect(color=NA, fill = "#3c3c3c"))

mapfacet


```


```{r add in bar chart}

library(ggthemes)
# clustercols<-as_tibble(stack(colscale)) %>% 
#   mutate(across(is.factor, as.integer))
#   
# 
# maptexts<-top_cities %>% 
#   left_join(clustercols, by=c("cluster"="ind"))

rightbars<-ggplot(top_cluster_IPA) +
    geom_col(aes(x=reorder(max_city, cluster_IPA_size), 
                       y=cluster_IPA_size, 
                       fill=as.factor(cluster))) +
    scale_fill_manual(values=colscale) +
    coord_flip() +
    theme_clean() +
    facet_wrap(~IPA, ncol=1, scales="free") +
    labs(x="",y="Medals in Cluster",
         title="Medals by Cluster Top City and Beer Type") +
    theme(legend.position = "none",
          plot.title =element_text(color="white", family="Candara", face="bold", size=14, hjust = 0.5, margin=margin(0,5,0,0)),
          panel.border = element_blank(),
          axis.text=element_text(color="white",  family="Candara", face="bold", size=12),
          axis.title =element_text(color="white",  family="Candara",face="bold", size=14),
          strip.text = element_text(color="white",  family="Candara", face="bold", size=14),
          strip.background = element_rect(fill = "#3c3c3c"),
          plot.background = element_rect(fill = "#3c3c3c", color=NA),
          panel.background = element_rect(fill = "#3c3c3c", color=NA))

  
rightbars

library(patchwork)
mapfacet + rightbars




```

```{r plot it out}

library(ggtext)

bottom<-(mapfacet + rightbars) +  plot_layout(ncol = 2, widths = c(7,4))

library(ragg)
#install.packages("systemfonts")
library(systemfonts)


mytheme<-theme(
      plot.title = element_markdown(size = 22, 
                          hjust=0.5,
                          family="Candara",
                          fill= "#3c3c3c",
                          margin=margin(3,0,4,0),
                          color="white",
                          face = "bold"),
      plot.subtitle = element_markdown(
                          size=16,
                          family="Candara",
                          hjust=0.5,
                          face="bold",
                          color="white",
                          fill="#3c3c3c",
                          lineheight = 1),
      plot.caption = element_markdown(
                          size=12,
                          family="Candara",
                          hjust=0.5,
                          face="bold",
                          color="white",
                          fill="#3c3c3c",
                          lineheight = 1),
      panel.background=element_rect(fill = "#3c3c3c", color=NA),
      plot.background = element_rect(fill = "#3c3c3c", color=NA))


final<-bottom +
  plot_annotation(
    title="*Where's The Hops?* Regionality of Great American Beer Festival Awards, 1987-2020",
    subtitle="The annual competition has awarded 4,970 medals to 1,859 breweries. When locating those breweries by city, <br> clusters emerge around Southern California, the Pacific Northwest, the Atlantic North East, Colorado, and Chicago/Milwaukee. <br> But the *tastiest* and *hoppiest* beers often found along the California coast!",
    caption = "Locations are geocoded with OSM and clustered by {dbscan} package. Black circles could not be clustered. <br> Excludes 79 medals from Alaska and Hawaii, and 24 medals in lower 48 that could not be geocoded. <br> City circles sized from 1 medal to 129 medals (in Denver). <br>Data: GABF - Design: @1ambodo",
    theme=mytheme)
    

library(patchwork)

final

#for captions
# beer_awards %>% filter(state %in% c("AK","HI"))
# 
# map_data_raw %>% filter(centroid==T)
# 
# map_data %>% filter(n==max(n))

```

```{r finish}


#Finish!
agg_png("p.png", width = 1200, height = 700, units = 'px')
final
dev.off()


```


